---
title: "Assignment B-1"
author: "Serena Choi"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load pacakges & Choose dataset

We will first load the required packages. 
```{r}
library(tidyverse)
library(testthat)
library(datateachr)
```

For this analysis, I would like to use "flow_sample" dataset. 

```{r}
glimpse(flow_sample)
```

## Exercise 1. Make a Function

I will define a function "annual_flow_gap" as the difference between annual maximum flow and minimum flow. 

```{r}
annual_flow_gap <- function (data, x, y, na.rm = TRUE) {
  data %>%
    group_by(x) %>%
    summarise(flow_gap = max(y) - min(y)) %>%
    ggplot(aes(x = x, y = flow_gap)) +
    geom_line()
  
annual_flow_gap(flow_sample, 1990, flow)
```




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
