---
title: "Assignment B-1"
author: "Serena Choi"
date: "11/1/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load pacakges & Choose dataset

We will first load the required packages. 
```{r}
library(tidyverse)
library(testthat)
library(datateachr)
```

For the following exercises, I will use a pivoted version of "flow_sample" that would make executing my function much easier. I will call this new data frame as "pivoted_flow_sample". 
```{r}
glimpse(flow_sample)
```

```{r}
pivoted_flow_sample <- flow_sample %>%
  pivot_wider("year", names_from = "extreme_type", values_from = "flow") %>%
  group_by(year) %>%
  mutate(maximum = as.numeric(maximum)) %>%
  mutate(minimum = as.numeric(minimum)) 

head(pivoted_flow_sample)
```

## Exercise 1 & 2. Make & Document Functions 


I will define a function "annual_flow_gap" as the difference between annual maximum flow and minimum flow.
```{r}
#'Annual flow gap function (annual_flow_gap)
#'
#' This function is to find a delta value, which is the difference
#' between the annual maximum flow and minimum flow. 
#'
#' @param data is a data set to use. 
#' @param x is the maximum flow value. 
#' @param y is the minimum flow value. 
#' @return "flow_gap" creates the table of outputs that are the difference between maximum and minimum flows for each year. 
#' @example annual_flow_gap(pivoted_flow_sample, pivoted_flow_sample$maximum , pivoted_flow_sample$minimum)

annual_flow_gap <- function (data, x, y) {
  delta_wrap <- data %>% summarise(delta = data[[{{x}}]] - data[[{{y}}]])   %>%
    drop_na()
  return(delta_wrap)
}

```


```{r}
flow_gap_result <- annual_flow_gap(data = pivoted_flow_sample, x = "maximum", y = "minimum") 
head(flow_gap_result)
```

## Exercise 3. Include examples

example 1: when x is not a numeric value, you get an error. 
```{r, error = TRUE}
example_1 <- annual_flow_gap(flow_sample, x = "sym", y = "flow")

```

example 2: when y is not a numeric value, you get an error. 
```{r, error = TRUE}
example_2 <- annual_flow_gap(flow_sample, x = "flow", y = "extreme_type")
```

example 3: Using a different data frame, "mtcars", I will find differences between two numerical values.  
```{r}
glimpse(mtcars)
example_3 <- annual_flow_gap(mtcars, x = "disp", y = "hp")
head(example_3)
```

## Exercise 4. Test Functions 
When we run the function to the data frame, the created column name is delta. 
```{r}
test_that("Column name is delta", {
  expect_named(annual_flow_gap(data = pivoted_flow_sample, x = "maximum", y = "minimum"), c("year", "delta"))
})
```

When we run the data set with non-numeric values, we expect errors. 
```{r}
test_that("Has a error due to non-numeric values", {
  expect_error(annual_flow_gap(flow_sample, x = "sym", y = "flow"))
})
```

When we run the function to the data frame, the vector length is always 2. 
```{r} 
test_that("Vector of length 2", {
  expect_length(annual_flow_gap(data = pivoted_flow_sample, x = "maximum", y = "minimum"), 2)
})
  
```